Elite individuals, insitutions, and economic growth accounting

### 2024-04-08 presentation/main.tex
fix some typos, remote distribution slide

\begin{frame}{Table of Contents}
    \tableofcontents
\end{frame}
\section{Intro}
\begin{frame}
    \frametitle{Research Question}
    \begin{block}{What is the relationship between elite students, academic institutions, and economic growth?}
        \begin{itemize}
            \item Are there outsized returns to economic growth when there are more academic elites?
            \item How can we measure academic competition and education quality beyond means?
        \end{itemize}
    \end{block}
    \begin{exampleblock}{Method}
        Through this paper, I investigate the relationship between the number of top-ranked universities, share of top math students,
        IMO scores, and GDP per capita growth to analyze these questions.
    \end{exampleblock}
\end{frame}

@@

\begin{frame}
    \frametitle{World Bank Data}
    \framesubtitle{Distributions}
    \centering
    \includegraphics[width=\textwidth]{../charts/wdi.png}
\end{frame}

@@

\section{Empirical Results}
\begin{frame}{Model specification}
    Let elite indicators be: $math99, ARWU, IMO$.
    For the sake of concision, let $E_{i,t}$ be a 1 by 4 matrix defined as:
    \[E_{i,t} = 
    \begin{bmatrix}
        math99_{i, t} & ARWU_{i, t} & IMO_{i, t}
    \end{bmatrix}
    \] for country/region $i$ in year $t$.
    Let the coefficients of $E_{i, t}$ be a 4 by 1 matrix called $\lambda$. For control variables, $I_{i, t}$ is the matrix of variables and $\alpha$ is coefficients.
    \begin{equation}
        Y_{i, t} = \beta_0 + \lambda E_{i, t} + \delta GDPpc \times E_{i,t} + \alpha I_{i, t} + T_t + C_i + \epsilon_{i, t}
    \end{equation}
    where $T,C$ represent time and entity dummies respectively and $Y_{i,t}$ be the GDP per capita growth in basis points for a country/region $i$ and year $t$.

>>>>

\begin{frame}{Table of Contents}
    \tableofcontents
\end{frame}
\section{Intro}
\begin{frame}
    \frametitle{Research Question}
    \begin{block}{What is the relationship between elite students, academic institutions, and economic growth?}
        \begin{itemize}
            \item Are there outsized returns to economic growth when there are more academic elites?
            \item How do these indicators interact with GDP per capita? Are some more helpful for growth than others?
        \end{itemize}
    \end{block}
    \begin{exampleblock}{Method}
        Through this paper, I investigate the relationship between the number of top-ranked universities, share of top math students,
        IMO scores, and GDP per capita growth to analyze these questions.
    \end{exampleblock}
\end{frame}

@@

% \begin{frame}
%     \frametitle{World Bank Data}
%     \framesubtitle{Distributions}
%     \centering
%     \includegraphics[width=\textwidth]{../charts/wdi.png}
% \end{frame}

@@

\section{Empirical Results}
\begin{frame}{Model specification}
    Let elite indicators be: $math99, ARWU, IMO$.
    For the sake of concision, let $E_{i,t}$ be a 1 by 4 matrix defined as:
    \[E_{i,t} = 
    \begin{bmatrix}
        math99_{i, t} & ARWU_{i, t} & IMO_{i, t}
    \end{bmatrix}
    \] for country/region $i$ in year $t$.
    Let the coefficients of $E_{i, t}$ be a 3 by 1 matrix called $\lambda$. For control variables, $I_{i, t}$ is the matrix of variables and $\alpha$ is coefficients.
    \begin{equation}
        Y_{i, t} = \beta_0 + \lambda E_{i, t} + \delta GDPpc \times E_{i,t} + \alpha I_{i, t} + T_t + C_i + \epsilon_{i, t}
    \end{equation}
    where $T,C$ represent time and entity dummies respectively and $Y_{i,t}$ be the GDP per capita growth in basis points for a country/region $i$ and year $t$.
